%-------------------------
% Resume in Latex
% Author: Vaishanth (modified for two-page layout with projects)
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\colorlet{name}{black}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{black}
\colorlet{body}{black}

%----------FONT OPTIONS----------
\usepackage{charter}
\usepackage[scaled=.95]{helvet} % For sans-serif headings

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectItem}[2]{
  \item\small{
    \textbf{#1:} #2 \vspace{-1pt}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in, itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------------------------%
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\LARGE Om Prakash Peddamadthala} \\
    \vspace{2pt}
    \small
    {+91 98481 49507} $\cdot$
    \href{[url to portfolio]}{\color{blue}{Portfolio}} $\cdot$
    \href{mailto:omprakashornold@gmail.com}{\color{blue}{omprakashornold@gmail.com}} $\cdot$
    \href{https://www.linkedin.com/in/omprakash-peddamadthala/}{\color{blue}{linkedin.com/in/omprakash-peddamadthala}} $\cdot$
    \href{https://github.com/omprakashpeddamadthala}{\color{blue}{github.com/omprakashpeddamadthala}} \\
    \vspace{-5pt}
\end{center}

%-----------SUMMARY-----------
\section{\color{airforceblue}Professional Summary}
\resumeItemListStart
\resumeItem{Software Engineer with 5+ years of experience in designing and developing robust solutions using Java, Spring Boot, and Microservices.}
\resumeItem{Skilled in building scalable systems, focusing on real-time data processing, API development, and third-party integrations.}
\resumeItem{Proficient in CI/CD pipelines, Docker, Jenkins, SonarQube, and JIRA for system management and quality assurance.}
\resumeItem{Collaborates effectively with cross-functional teams to deliver high-quality solutions aligned with business goals.}
\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{\color{airforceblue}Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      \textbf{Languages:} Java, Groovy, SQL \\
      \textbf{Frameworks:} Spring, Spring Boot, Grails, Hibernate, JPA \\
      \textbf{Build Tools:} Maven, Gradle \\
      \textbf{IDE:} IntelliJ IDEA, Visual Studio Code, Jasper Studio \\
      \textbf{Web Technologies:} HTML, CSS, JavaScript, jQuery, React (Basics) \\
      \textbf{Databases:} MySQL, PostgreSQL \\
      \textbf{OS:} Windows 11, Unix, Linux \\
      \textbf{Tools:} AWS, SonarQube, Jenkins, Git, JIRA, Docker, Postman, Swagger \\
    }}
\end{itemize}

%-----------WORK EXPERIENCE-----------
\section{\color{airforceblue}Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Engineer}{Hyderabad, Telangana}
{Computer Generated Solutions Pvt Ltd}{Aug 2023 - Present}
\resumeItemListStart
\resumeItem{Developed Threadvine B2B ecommerce platform, enhancing digital catalog management and real-time inventory tracking using Spring Boot.}
\resumeItem{Integrated SendGrid API for email management, streamlining communication and tracking email logs.}
\resumeItem{Implemented order management logic and complex business rules for order placement.}
\resumeItem{Introduced AOP for user activity tracking, improving system monitoring without codebase changes.}
\resumeItem{Fixed bugs and developed features based on client needs, ensuring timely delivery.}
\resumeItem{Collaborated on feature design to enhance performance and user experience.}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{Chennai, Tamilnadu}
{Platform 3 Technologies Pvt Ltd}{Aug 2022 - July 2023}
\resumeItemListStart
\resumeItem{Designed services for data extraction in Archon ETL platform, migrating and archiving data from DB2 to EDB and PostgreSQL.}
\resumeItem{Integrated OpenText API to automate Excel file uploads, ensuring smooth data transformation and migration.}
\resumeItem{Collaborated on backend processes to support UI requirements, ensuring seamless data flow.}
\resumeItem{Prepared product documentation and developed JUnit test cases for robust backend services.}
\resumeItem{Deployed builds in Linux environments using Docker for reliable deployments.}
\resumeItemListEnd

\resumeSubheading
{Jr. Java Developer}{Hyderabad, Telangana}
{Aldrich Research Services Pvt Ltd}{Dec 2019 - July 2022}
\resumeItemListStart
\resumeItem{Developed web crawlers using JSOUP to extract and parse data, improving data collection efficiency.}
\resumeItem{Built RESTful web services with Spring Boot for interaction with external systems.}
\resumeItem{Integrated API responses and parsing for accurate data extraction and presentation.}
\resumeItem{Managed MySQL and MongoDB databases, optimizing queries for faster retrieval.}
\resumeItem{Developed POJOs and persistence layers using Hibernate, and contributed to Spring MVC views.}
\resumeItem{Implemented Log4J for logging and error tracking across systems.}
\resumeItem{Participated in daily scrum meetings to resolve issues and meet project deadlines.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{\color{airforceblue}Education}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Computer Science and Engineering}{Hyderabad, Telangana}
{St. Mary's Group of Institutions}{Aug 2014 - July 2018}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\color{airforceblue}Projects}
\resumeItemListStart
\resumeProjectItem{Event Ticket Booking Platform}{Developed a web application using Spring Boot and PostgreSQL for booking event tickets, featuring user authentication and payment integration.}
\resumeProjectItem{Ecommerce Application}{Built a B2C ecommerce platform with Spring Boot, Hibernate, and PostgreSQL, supporting product catalog and order processing.}
\resumeProjectItem{Blog Application}{Created a blogging platform using Grails and MySQL, enabling users to publish and manage posts with a responsive UI.}
\resumeItemListEnd

\end{document}
